Optimal (Multiway) Spatial Joins

### 2024-05-24 msj.tex
yufei

Lemma~\ref{lmm:hv:type1:properties} assures us that the set $\J^*$ thus computed indeed satisfies \eqref{eqn:hv:type1:J*}. Furthermore, if we are given $\cross(\bm{t}, H)$ and $\cross(\bm{t}, V)$ for each $\bm{t}$, Lemma~\ref{lmm:hv:type1:properties} further asserts that the above algorithm runs in $O(1 + |\J^*|) = O(1 + \out)$ time.

>>>>

Lemma~\ref{lmm:hv:type1:properties} assures us that the set $\J^*$ thus computed indeed satisfies \eqref{eqn:hv:type1:J*}. Furthermore, if we are given $\cross(\bm{t}, H)$ and $\cross(\bm{t}, V)$ for each $\bm{t}$, Lemma~\ref{lmm:hv:type1:properties} further asserts that the above algorithm runs in $O(1 + k \cdot |\J^*|) = O(1 + k \cdot \out)$ time.

The rest of the section will focus on explaining how to prepare the sets $\cross(\bm{t}, H)$ of all $\bm{t} \in \J(R_1', ..., R_{k-2}')$ in $O(n \log n + k \cdot \out)$ time. An analogous algorithm can be used to compute the sets $\cross(\bm{t}, V)$ of all $\bm{t}$ in the same time complexity.
